### 2012-05-09 GUIErrorDetector/paper/conclusion.tex
Mike's edits through section 4.1

\section{Conclusion and Future Work}

In this paper, we presented a general technique to find invalid
thread access errors for multithreaded GUI applications. 
Our technique statically explores paths in a call graph to check
whether a non-UI thread can access a GUI object.
It uses a reflection-aware call graph construction algorithm
to build a good call graph, and employs a set of error
filters to filter likely false positives and redundant warnings.
%Since graphical user interfaces are often inadequately tested due
%to the enormously large space of UI interactions and
%extreme resource constraints during their development, we
%believe that providing a static analysis can allow developers to find
%more potential errors %before the application is released to customers (XXX),
% to improve software reliability.
We demonstrated the usefulness of our technique
by an evaluation on \subnum subjects on 4 popular GUI
frameworks. 
%Our experiments have shown that we can find bugs
%in real-world programs.

Besides general issues such as performance or ease of use, our future
work will concentrate on the following topics:

%\begin{itemize}
%\item
\textbf{Integration with dynamic and symbolic analyses.} The technique 
presented in this paper is a call graph-based, pure static analysis. 
It suffers from false positives for many GUI applications,
due to the conservative nature of static analysis.
A possible way to reduce the number of false
positives is to integrate with
dynamic analyses~\cite{Jiang:2008:PPS:1453101.1453110}%, ZhangSBE2011}
or symbolic analyses~\cite{xie05:symstra, Pasareanu:2011, halfond09issta, BMF97}
by using more accurate information to guide call graph exploration.

%\item
\textbf{Unit testing multithreaded GUI programs.} Besides
a static analysis,  software testing is another
way to improve software quality.  Although many
testing techniques have been developed recently, few of them can be applied
to unit test multithreaded GUI programs to find potential errors \textit{earlier}. We
plan to investigate how to apply recent advance in automated
testing~\cite{Staats:2011:PTO:1985793.1985847, Jagannath:2011:IMU:2025113.2025145, Muccini_Bertolino_Inverardi_2004, Ricca:2001:ATW:381473.381476, Harman:2007}
to the context of multithreaded GUI applications.

%\item
\textbf{Fixing potential GUI errors.} After an error is revealed, fixing
it and verifing the patch has often been another important and time-consuming process. Fixing concurrency
bugs has become especially critical in the multicore era.
Recently, a few work has been done
on automatically repairing test script for GUI applications~\cite{Daniel:2011:AGR:2002931.2002937, Huang:2010:RGT:1828417.1828465}. However, none of them focuses on repairing
the GUI program to patch a revealed error. Thus, we are interested in 
developing automated error fixing techniques for
multithreaded GUI applications.

@@

>>>>

\smallstep
\section{Conclusion and Future Work}

This paper presented a general technique to find invalid
thread access errors in multithreaded GUI applications. 
Our technique statically explores paths in a call graph to check
whether a non-UI thread can access a GUI object.
It uses a reflection-aware call graph construction algorithm
to build a good call graph, and employs a set of error
filters to filter likely false positives and redundant warnings.
We demonstrated the usefulness of our technique
by an evaluation on \subnum programs built on 4 popular GUI
frameworks.

The source code of our tool implementation is available at:

\noindent \url{http://guierrordetector.googlecode.com}

\vspace{1mm}

Besides general issues such as performance and ease of use, our future
work will concentrate on the following topics:

%\begin{itemize}
%\item
\textbf{Integration with dynamic and symbolic analyses.} The technique 
presented in this paper is a call graph-based, pure static analysis. 
It suffers from false positives for many GUI applications,
due to the conservative nature of static analysis.
A possible way to reduce the number of false
positives is to integrate with
dynamic analyses~\cite{ZhangSBE2011}
or symbolic analyses~\cite{xie05:symstra, Pasareanu:2011}
by using more accurate information to guide call graph exploration.

%\item
\textbf{Unit testing multithreaded GUI programs.} Besides
a static analysis,  software testing is another
way to improve software quality.  Although many
testing techniques have been developed recently, few of them can be applied
to unit test multithreaded GUI programs to find potential errors \textit{earlier}. We
plan to investigate how to apply recent advance in automated
testing~\cite{ZhangSBE2011, Jagannath:2011:IMU:2025113.2025145}
to the context of multithreaded GUI applications.

%\item
\textbf{Fixing potential GUI errors.} After an error is revealed, fixing
it and verifying the patch is often time-consuming. Fixing concurrency
bugs has become especially critical in the multicore era.
Recently, work has been done
on automatically repairing test scripts for GUI applications~\cite{Daniel:2011:AGR:2002931.2002937, Huang:2010:RGT:1828417.1828465}. However, none of them focuses on repairing
the GUI program to patch a revealed error. Thus, we are interested in 
developing automated error fixing techniques for
multithreaded GUI applications.

@@

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "guierror"
%%% TeX-command-default: "PDF"
%%% End:

%  LocalWords:  multithreaded multicore

### 2012-05-09 GUIErrorDetector/paper/evaluation.tex
Mike's edits through section 4.1

We used a set of open-source projects from SourceForge, Google Code
and the Eclipse plugin marketplace as evaluation subjects.

Five subjects (EclipseRunner, HudsonEclipse, SGTPuzzler, Fennec, and MyTracks)
have known invalid thread access errors, all of which have been fixed later.
We ran our tool on the reported buggy versions to check whether it
can correctly identify the existing errors. 
We selected the other five subjects by first searching for the
framework keywords (e.g., ``Java Swing'' or ``Java SWT'')
in the above source repositories, and then chosing subjects based on the following
criteria. First, the subject must be a Java application, not
an open library. Second, the subject must use multithreading in its implementation.
Third, the subject is listed in the first 5 result pages.
This permits us to exclude immature subjects that may contain obvious errors.
We ran our tool on the latest stable release of each project to check whether
it can find any new errors.

@@

\end{center}
\vspace{-15pt}
\Caption{{\label{table:subjects} Open source programs
used in our evaluation. Column ``LOC'' is the number of non-blank, non-comment lines
of code, as counted by LOCC~\cite{locc}.  Each program is analyzed
together with its GUI framework, as listed in
the bottom table.} }
\end{table}

@@

We first inspected the source code of each subject to determine whether any
native methods or project-specific GUI interaction patterns were implemented.
Only SGTPuzzler uses native methods to interact with
the underlying operating system. For it, we manually checked the possible
Java methods that a native method may call, and then added \annotationnum \CodeIn{@CalledByNativeMethods}
annotations for it. 
%Two subjects, MyTracks and Fennec, employ a customized pattern
%to interact with the GUI framework. For example, in MyTracks, all non-UI
%threads are initialized via using the library method \CodeIn{android.os.}\discretionary{}{}{}\CodeIn{handler.handleCallback}.
% the \CodeIn{safeInvokeXX}
%method in the XXX subject first checks whether the current thread is the UI-thread, and
%then determines whether to direct access a GUI object or wrap the code with
%message passing. 
We also added \filternum user-defined filters for two subjects
(MyTracks and Fennec), since they use a customized pattern
to interact with the GUI framework.
In this experiment, none of the paper
authors was familiar with the subjects, but we found it was quite easy
to add extra annotations and user-defined filters. All these
manual parts took less than a total of 60 minutes.

For all \subnum programs, we manually determined the validity of each output warning
by either searching the bug repository to check it with the bug-fixing revision history,
or submitting a new bug report, or writing a test driver to reproduce
the error.

@@

As shown in Table~\ref{table:results}, our tool found
errors in each subject. Using the 1-CFA
call graph algorithm, our tool issued 22 warnings, among
which \bugs warnings reveal \bugs distinct errors (\newbugs were previously unknown),
2 warnings are false positives, and the remaining 8 warnings
are redundant. Section~\ref{sec:reflectionaware} compares with other call graph
construction algorithms.

%After checking against existing patches, we found
Our tool correctly identified the \oldbugs known errors, as compared to
their patches.
We submitted all \newbugs new errors
to the subject developers. As of April 2012, 1 error in S3dropbox has been confirmed,
we have reproduced 3 errors, and 3 errors in VirgoFTP, FileBunker and ArecaBackup
had not yet been verified by the developers.

@@

%Figures~\ref{fig:swingerror} amd~\ref{fig:pluginerror} show
%two real errors our tool has found. 
Figure~\ref{fig:swingerror}
shows an invalid thread access error our tool found in S3dropbox.
This error happens when the \CodeIn{deleteCurrentBucket}
call on line 63 throws an exception, making it hard to
detect by testing. We reported this error to the S3dropbox developers. Tom Czarniecki,
a key developer of S3dropbox, confirmed this single-GUI-thread
violation. He mentioned that the S3dropbox project uses
certain design patterns to avoid such violations (e.g.,
actions for UI interaction are encapsulated into a \CodeIn{Worker} interface),
but the developers still overlooked  the error our tool found.
Another reason they overlooked this violation is because some GUI frameworks like Swing
do not provide any runtime checks for invalid thread accesses. The Swing
GUI does not exhibit user-visible faults on some erreoneous executions.
However, as clearly stated in the official documentation~\cite{swing}, %Swing is a single-GUI-threaded GUI toolkit and
accessing Swing GUI objects from non-UI threads risks thread interference
or memory-consistency errors.

@@

Besides the above two examples, other errors our tool reported are also
subtle to find. For example, our tool found two new errors in SudokuSolver.
One error only happens when
the given Sudoku is unsolvable; and the other one happens
when the program fails to launch the mail composing window of the
user's default mail client (i.e., the \CodeIn{java.awt.Desktop.mail()}
method throws an exception after a user clicks the "eMail Me" button).

@@

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.44]{cgexample}
  \vspace*{-5.0ex}\caption {{\label{fig:ex} (a) shows example code, in which
\CodeIn{safe()} is a Safe UI method, and \CodeIn{uiAcc()} is a UI-accessing method.
(b) shows a less precise call graph built by RTA or 0-CFA, and (c) shows a more
precise call graph built by 1-CFA. Nodes for constructors are omitted for brevity.
\newline
Using the less precise call graph, our error
detection algorithm (Figure~\ref{fig:detectalgorithm}) reports an invalid method
call chain: \CodeIn{entry()}
$\rightarrow$ \CodeIn{f()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{run()}
$\rightarrow$ \CodeIn{uiAcc()}. It does not report
the actual error path because it is longer: \CodeIn{entry()} $\rightarrow$ \CodeIn{g1()} $\rightarrow$
\CodeIn{g2()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{run()} $\rightarrow$ \CodeIn{uiAcc()}.
The algorithm outputs the actual error path when using the more precise call graph.
}}
\end{figure}

@@

Given a sound call graph, suppose that there exists some
error-revealing path between an entry node E and a UI-accessing node U.  A sound
search strategy is one that reports some error-revealing path between
E and U, while  an unsound strategy might report an infeasible
path between the nodes.  Exhaustive search is sound because it does not
miss any possible paths.  However, it is impractical.  Compared to
exhaustive search, BFS or DFS is unsound because they visit
every node, but do not traverse \textit{every} path to visit that node.
Using BFS or DFS can be viewed as a heuristic filtering
step, akin to the filters of Section~\ref{sec:heuristic}.
% The heuristics of Section~\ref{sec:heuristic} are
%more effective at retaining real errors than the search variants.
%Given a sound call graph, exhaustive search is sound because it does not
%miss any possible errors.  However, it is impractical.  Compared to
%exhaustive search, using BFS or DFS can be viewed as a heuristic filtering
%step, akin to the filters of Section~\ref{sec:heuristic}.
%The heuristics of Section~\ref{sec:heuristic} are
%more effective at retaining real errors than the search variants.

@@

\noindent \textbf{\textit{Performance and scalability.}} Our tool
has been evaluated on \subnum subjects with over \totaloc LOC and frameworks
with 1.4 MLOC, showing good scalability. Our evaluations
were conducted on a 2.67GHz Intel Core PC with 4GB
physical memory (1GB is allocated for JVM), running Windows 7.
For the most time-consuming subject, S3dropbox, our tool finished the whole analysis
within 252 seconds using the most expensive 1-CFA call graph construction
algorithm. Analyzing other subjects using different algorithms took less time.
Call graph construction took 33--91\% of the total time.

@@

%  LocalWords:  multithreaded SWT multithreading 2mm VirgoFTP UI GMail S3
%  LocalWords:  FileBunker ArecaBackup plugins HudsonEclipse EclipseRunner
%  LocalWords:  S3dropbox SudokuSolver Sudoku mutlithreaded SGTPuzzler 9pt
%  LocalWords:  Fennec MyTracks LOC v9306 plugin LOCC RTA CFA
%  LocalWords:  CalledByNativeMethods

>>>>

We used 10 open-source projects from SourceForge, Google Code,
and the Eclipse plugin marketplace as evaluation subjects.

Five subjects (EclipseRunner, HudsonEclipse, SGTPuzzler, Fennec, and MyTracks)
are selected because they have known invalid thread access errors (1 error per subject) and
all errors have been fixed in later revisions.
We used the buggy versions to check whether our tool
can correctly identify those known errors. 
For the other five subjects, we selected them
by first searching for the
framework keywords (e.g., ``Java Swing'' or ``Java SWT'')
in the above source repositories, and then choosing subjects based on the following
criteria. First, the subject must be a Java application, not
an open library. Second, the subject must use multithreading in its implementation.
Third, the subject is listed in the first 5 result pages.
This permits us to exclude immature subjects that may contain obvious errors.
For each selected subject, we ran our tool on the latest stable release to find new errors.
%of each project to check whether
%it can find any new errors.

@@

\end{center}
\vspace{-15pt}
\Caption{{\label{table:subjects} Open-source programs
used in our evaluation. Column ``LOC'' is the number of non-blank, non-comment lines
of code, as counted by LOCC~\cite{locc}.  Each program is analyzed
together with its GUI framework, as listed in
the bottom table.} }
\end{table}

@@

%We first inspected the source code of each subject to determine whether any
%native methods or project-specific GUI interaction patterns were implemented.

Subject SGTPuzzler uses native methods to interact with
the underlying operating system. For it, we manually checked the possible
Java methods that a native method may call, and then added \annotationnum \CodeIn{@CalledByNativeMethods}
annotations for it. 
During experiment, we found two subjects (MyTracks and Fennec)
use a customized pattern to interact with the GUI framework.
For them, we added \filternum user-defined filters.
In this experiment, none of the paper
authors was familiar with the subjects, but we found it was quite easy
to add extra annotations and user-defined filters. All these
manual parts took less than a total of 60 minutes.

For all \subnum programs, we manually determined the validity of each output warning
by either searching the bug repository to check bug-fixing revision histories,
or submitting a new bug report, or writing a test driver to reproduce
the error.

@@

As shown in Table~\ref{table:results}, our tool found
errors in each subject. Using the 1-CFA
call graph algorithm, our tool issued 22 warnings, among
which \bugs warnings reveal \bugs distinct errors (\newbugs were previously unknown,
and the \oldbugs known errors were correctly identified),
2 warnings are false positives, and the remaining 8 warnings
are redundant. Section~\ref{sec:reflectionaware} compares with other call graph
construction algorithms.

%After checking against existing patches, we found
%Our tool correctly identified the \oldbugs known errors, as compared to
%their patches.
We submitted all \newbugs new errors
to the subject developers. As of April 2012, 1 error in S3dropbox has been confirmed,
we have reproduced 3 errors, and 3 errors in VirgoFTP, FileBunker and ArecaBackup
had not yet been verified by the developers.

@@

%Figures~\ref{fig:swingerror} amd~\ref{fig:pluginerror} show
%two real errors our tool has found. 
Figure~\ref{fig:swingerror}
shows an invalid thread access error our tool found in S3dropbox.
This error happens when the \CodeIn{deleteCurrentBucket}
call on line 63 throws an exception, making it hard to
detect by testing. We reported this error to the S3dropbox developers. Tom Czarniecki,
a key developer of S3dropbox, confirmed this single-GUI-thread
violation. He mentioned that the S3dropbox project uses
certain design patterns to avoid such violations (e.g.,
actions for UI interaction are encapsulated into a \CodeIn{Worker} interface),
but the developers still overlooked  the error our tool found.
Another reason they overlooked this violation is because some GUI frameworks like Swing
do not provide any runtime checks for invalid thread accesses. The Swing
GUI does not exhibit user-visible faults on some erroneous executions.
However, as clearly stated in the official documentation~\cite{swing}, %Swing is a single-GUI-threaded GUI toolkit and
accessing Swing GUI objects from non-UI threads risks thread interference
or memory-consistency errors.

@@

Besides the above two examples, other errors our tool reported are also
subtle to find. For example, our tool found two new errors in SudokuSolver.
One error only happens when
the given Sudoku is unsolvable; and the other one happens
when the program fails to launch the mail composing window of the
user's default mail client (i.e., the \CodeIn{java.awt.Desktop.mail()}
method throws an exception after a user clicks the ``eMail Me'' button).

@@

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.44]{cgexample}
  \vspace*{-5.0ex}\caption {{\label{fig:ex} (a) shows example code, in which
\CodeIn{safe()} is a Safe UI method, and \CodeIn{uiAcc()} is a UI-accessing method.
(b) shows a less precise call graph built by RTA or 0-CFA, and (c) shows a more
precise call graph built by 1-CFA\@. Nodes for constructors are omitted for brevity.
\newline
Using the less precise call graph, our error
detection algorithm (Figure~\ref{fig:detectalgorithm}) reports an invalid method
call chain: \CodeIn{entry()}
$\rightarrow$ \CodeIn{f()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{run()}
$\rightarrow$ \CodeIn{uiAcc()}. It does not report
the actual error path because it is longer: \CodeIn{entry()} $\rightarrow$ \CodeIn{g1()} $\rightarrow$
\CodeIn{g2()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{run()} $\rightarrow$ \CodeIn{uiAcc()}.
The algorithm outputs the actual error path when using the more precise call graph.
}}
\end{figure}

@@

Given a sound call graph, suppose that there exists some
error-revealing path between an entry node E and a UI-accessing node U\@.  A sound
search strategy is one that reports some error-revealing path between
E and U, while  an unsound strategy might report an infeasible
path between the nodes.  Exhaustive search is sound because it does not
miss any possible paths.  However, it is impractical.  Compared to
exhaustive search, BFS or DFS is unsound because they visit
every node, but do not traverse \textit{every} path to visit that node.
Using BFS or DFS can be viewed as a heuristic filtering
step, akin to the filters of Section~\ref{sec:heuristic}.
% The heuristics of Section~\ref{sec:heuristic} are
%more effective at retaining real errors than the search variants.
%Given a sound call graph, exhaustive search is sound because it does not
%miss any possible errors.  However, it is impractical.  Compared to
%exhaustive search, using BFS or DFS can be viewed as a heuristic filtering
%step, akin to the filters of Section~\ref{sec:heuristic}.
%The heuristics of Section~\ref{sec:heuristic} are
%more effective at retaining real errors than the search variants.

@@

\noindent \textbf{\textit{Performance and scalability.}} Our tool
has been evaluated on \subnum subjects with \totaloc LOC and frameworks
with 1.4 MLOC, showing good scalability. Our evaluations
were conducted on a 2.67GHz Intel Core PC with 4GB
physical memory (1GB is allocated for JVM), running Windows 7.
For the most time-consuming subject, S3dropbox, our tool finished the whole analysis
within 252 seconds using the most expensive 1-CFA call graph construction
algorithm. Analyzing other subjects using different algorithms took less time.
Call graph construction took 33--91\% of the total time.

@@

%  LocalWords:  multithreaded SWT multithreading 2mm VirgoFTP UI GMail S3
%  LocalWords:  FileBunker ArecaBackup plugins HudsonEclipse EclipseRunner
%  LocalWords:  S3dropbox SudokuSolver Sudoku mutlithreaded SGTPuzzler 9pt
%  LocalWords:  Fennec MyTracks LOC v9306 plugin LOCC RTA CFA 9pt eMail g1
%  LocalWords:  CalledByNativeMethods deleteBucket deleteCurrentBucket g2
%  LocalWords:  deleteError showErrorMessage getSelectedBucketName uiAcc
%  LocalWords:  Czarniecki initializeResourceChangeListener getWorkspace
%  LocalWords:  ResourcesPlugin addResourceChangeListener resourceChanged
%  LocalWords:  IResourceChangeListener IResourceChangeEvent getViewer BFS
%  LocalWords:  ResourceChangeEvent msgTextView setLatLong TextView DFS
%  LocalWords:  findViewById setText getReachableStarts enqueueAll pushAll
%  LocalWords:  HundsonEclipse subcolumn MLOC 67GHz 4GB 1GB XTA VTA pre

### 2012-05-09 GUIErrorDetector/paper/implementation.tex
Mike's edits through section 4.1

We instantiated the proposed technique for four widely-used
GUI frameworks, namely SWT, Eclipse plugin framework, Swing, and Android;
and implemented an error detection tool on top of the WALA framework~\cite{walatutorial}.

@@

\begin{itemize}
\smallstep

\item \textbf{Call graph entry nodes:}  the main method. Like a normal Java program,
a SWT desktop application has a single main method as the entry point. By default,
the main method is executed in the UI thread after the GUI
is initialized.

@@

\item \textbf{UI-accessing nodes:}  the \CodeIn{Widget.checkWidget}
and \CodeIn{Display.}\discretionary{}{}{}\CodeIn{check}\discretionary{}{}{}\CodeIn{Device} methods. SWT performs
runtime checking before accessing a GUI object via these methods.
If the current thread is a non-UI thread, the \CodeIn{Widget.checkWidget}
and \CodeIn{Display.checkDevice} methods throw a \CodeIn{RuntimeException}.

@@

\item \textbf{Safe UI methods:}  \CodeIn{Display.asyncExec}
and \CodeIn{Display.syncExec}. SWT provides these two methods
to execute code (a)synchro- nizedly on the UI thread.

@@

\smallstep
\begin{myindentpar}{-2mm}

@@

\item \textbf{Call graph entry nodes:}  all user code methods that override
 SWT GUI event handling methods. Eclipse
calls back the overridden methods to handle the
events. All SWT GUI event handling methods (i.e., the overriden
methods in the class that implements \CodeIn{org.eclipse.swt.internal.SWTEventListener}) are
always called back from the UI thread.
%, thus are used as call graph entry nodes.

@@

\item \textbf{UI-accessing nodes} and \textbf{Safe UI methods} are the same as SWT.

\end{itemize}
\end{myindentpar}

@@

\begin{myindentpar}{-2mm}
\begin{itemize}
\tinystep

@@

\item \textbf{UI-accessing nodes:} %as stated in Swing's documentation,
all methods defined in each Swing GUI class except for three thread-safe
methods: \CodeIn{repaint()}, \CodeIn{revali-\\date()}, and \CodeIn{invalidate()}.

@@

\item \textbf{Safe UI methods:}  
\CodeIn{SwingUtilities.}\CodeIn{invokeLater} and \CodeIn{SwingUti-\\lities.invokeAndWait}, which execute code on the UI thread.

\end{itemize}
\end{myindentpar}

@@

\item \textbf{UI-accessing nodes:} the \CodeIn{ViewRoot.checkThread} method.
Like SWT, Android explicitly performs runtime checking before accessing
a GUI object via the \CodeIn{ViewRoot.checkThread} method. If the current
thread is a non-UI thread, the \CodeIn{ViewRoot.checkThread} method throws
a \CodeIn{RuntimeException}.

@@

\end{itemize}
\end{myindentpar}

@@

We implemented the reflection-aware call graph construction
 algorithm (Section~\ref{sec:cg}) using WALA's \textit{bypass logic}.
Unlike other tools~\cite{Payet:2011:SAA:2032266.2032299}, our tool
does not require a separate pass for program instrumentation; instead, it
parses the configuration file in an Android application,
and then intercepts the call graph construction
process on-the-fly to replace all reflection calls with object creation expressions.
Since Android applications are often fully encrypted and shipped in Dalvik
bytecode as a single apk file, our tool first uses
android-apktool~\cite{apktool} to
decrypt the apk file, and then uses the 
ded translator~\cite{ded} to convert
Dalvik bytecode to Java bytecode before feeding to WALA.  The Android system
library (i.e., \CodeIn{android.jar}) uses many ``stub'' classes as
placeholders for the sake of efficiency. We manually re-compiled 
\CodeIn{android.jar} from its source code, so it contains real
class files rather than stubs.

>>>>

We implemented an error detection tool on top of the WALA framework~\cite{walatutorial}.
We instantiated the proposed technique for four widely-used
GUI frameworks, namely SWT, Eclipse plugin framework, Swing, and Android.

@@

\preitemizespace

\item \textbf{Call graph entry nodes:}  the main method. 
% Like a normal Java program,
% a SWT desktop application has a single main method as the entry point. By default,
% the main method
It is executed in the UI thread after the GUI
is initialized.

@@

\item \textbf{UI-accessing nodes:}  the \CodeIn{Widget.checkWidget}
and \CodeIn{Display\-.check\-Device} methods.
% SWT performs
% runtime checking before accessing a GUI object via these methods.
% If the current thread is a non-UI thread, the \CodeIn{Widget.checkWidget}
% and \CodeIn{Display.checkDevice} methods throw a \CodeIn{RuntimeException}.
If the current thread is a non-UI thread, these
methods throw a \CodeIn{RuntimeException}.

@@

\item \textbf{Safe UI methods:}  \CodeIn{Display.asyncExec}
and \CodeIn{Display.syncExec}.
These methods
execute code (a)synchro\-nously on the UI thread.

@@

\preitemizespace

@@

\item \textbf{Call graph entry nodes:}  all user code methods that override
 SWT GUI event handling methods. Eclipse
calls back the overridden methods to handle the
events. All SWT GUI event handling methods (i.e., the overridden
methods in a class that implements \CodeIn{org.eclipse.swt.internal.SWTEventListener}) are
always called back from the UI thread.
%, thus are used as call graph entry nodes.

@@

\item \textbf{UI-accessing nodes} and \textbf{Safe UI methods} are the same as SWT\@.

@@

\preitemizespace

@@

\item \textbf{UI-accessing nodes:} %as stated in Swing's documentation,
all methods defined in each Swing GUI class except for three thread-safe
methods: \CodeIn{repaint()}, \CodeIn{reval\-i\-date()}, and \CodeIn{invalidate()}.

@@

\item \textbf{Safe UI methods:}  
\CodeIn{SwingUtilities.}\CodeIn{invokeLater} and \CodeIn{Swing\-Util\-ities.invokeAndWait}, which execute code on the UI thread.

@@

\item \textbf{UI-accessing nodes:} the \CodeIn{ViewRoot.checkThread} method.
% Like SWT, Android explicitly performs runtime checking before accessing
% a GUI object via the \CodeIn{ViewRoot.checkThread} method.
If the current
thread is a non-UI thread, the \CodeIn{ViewRoot.checkThread} method throws
a \CodeIn{RuntimeException}.

@@

@@

We implemented the reflection-aware call graph construction
 algorithm (Section~\ref{sec:cg}) using WALA's \textit{bypass logic}.
Unlike other tools~\cite{Payet:2011:SAA:2032266.2032299}, our tool
does not require a separate pass for program instrumentation; instead, it
parses the configuration file in an Android application,
and then intercepts the call graph construction
process on-the-fly to replace all reflection calls with object creation expressions.
Since Android applications are often fully encrypted and shipped in Dalvik
bytecode as a single apk file, our tool first uses
android-apktool~\cite{apktool} to
decrypt the apk file, and then uses the 
ded translator~\cite{ded} to convert
Dalvik bytecode to Java bytecode before feeding to WALA\@.  The Android system
library (i.e., \CodeIn{android.jar}) uses many ``stub'' classes as
placeholders for the sake of efficiency. We manually re-compiled 
\CodeIn{android.jar} from its source code, so it contains real
class files rather than stubs.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "guierror"
%%% TeX-command-default: "PDF"
%%% End:

%  LocalWords:  WALA SWT plugin checkWidget RuntimeException asyncExec apk
%  LocalWords:  syncExec synchro nously reval SwingUtilities invokeLater
%  LocalWords:  Util ities invokeAndWait ViewRoot checkThread postDelay
%  LocalWords:  WALA's Dalvik apktool ded
